\documentclass[margin]{res}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[colorlinks=true,pdfstartview=FitV,linkcolor=Blue,citecolor=Blue,urlcolor=Blue,filecolor=Blue]{hyperref}
\textwidth=5in

\begin{document}

%% \name{Lang Martin}
%% \address{lang.martin@gmail.com \quad\quad 423 521-0574}

\hbox to \hsize{%
\vbox{\raggedleft
{\bf Lang Martin}\\
lang.martin@gmail.com
423 521-0574\\
4412 St. Elmo Ave., Chattanooga TN 37409\\
\href{https://github.com/langmartin}{GitHub},
\href{http://www.linkedin.com/pub/lang-martin/0/bb1/611}{LinkedIn}%
}}

\begin{resume}
\section{About}

I am an expert software engineer and an engineering manager. I love
working in and building healthy development cultures. I'm interested
in programming languages and system architecture. I enjoy difficult
problems, elegant solutions, and a holistic approach to system design.

\section{\href{https://opentable.com/}{OpenTable}}

{\bf Principle Software Engineer}
%
Lead a team of five software engineers supporting the core business
restaurant operation software

Designed a built a synchronization proxy service providing
deterministic asynchronous data composition for 10k iPad clients

Designed and built an SMS messaging service used to notify diners in
thousands of restaurants

For both systems, I also managed the team that maintained the systems
once they were in production.
%
Dec 2013--Oct 2016

\section{\href{https://quickcue.com/}{Quickcue}}
o{\bf System Software Engineer}
%
Responsible for the design of the API, implementation of the API
server, and deployment strategy. A member of the initial product team,
also involved in planning of user interfaces. Quickcue was acquired by
OpenTable in 2013.\\
%
Dec 2011--Dec 2013

{\bf \href{https://www.cx.com/}{CX} Desktop Programming}
%
Development of the desktop syncing client. The client featured an
embedded Python interpreter that managed the API and file system, with
native wrappers for Windows and OS X.\\
%
Oct 2011--Dec 2011

{\bf \href{http://tva.gov/}{TVA} Internal Web Development}
%
Document storage interface, responsible for the specification,
estimation, design, implementation, deployment and support of three
medium-sized web interfaces to commercial database applications.\\
%
Apr 2009--Oct 2011

{\bf \href{http://thisismedium.com/}{Coptix} Programming and Architecture}
%
Initially system administration, then responsible for the deployment
strategy. In 2003, web development, working on ASP projects and
leading a shift to PHP. Helped design the new core tool set.
Instrumental in building a culture of experimentation. Coptix was
renamed `Medium' in 2009, and dissolved in 2011.\\
%
Sep 1999--Apr 2009

\section{Education}

Covenant College, graduated spring of 2000. A B.A.\ in
history with concentrations in education and mathematics.

\section{Technologies}

Clojure, Java, Linux,
PostgreSQL, MySQL, MS SQL Server,
JavaScript, Node.js, HTML5,
Scheme, Python, Perl, PHP, ASP,
Apache, HTTP, Git

\section{Projects}
{\bf Quickcue API} The Quickcue API stores a versioned data set for
synchronizing clients, enforcing the client's knowledge of the version
on updates, and broadcasting diffs to connected clients. It's written
in Clojure and uses PostgreSQL.

{\bf TVA DDS} The nuclear document distribution system is a
replacement for a custom mainframe application. The project was behind
schedule; designed the interface and application and launched on
schedule, allowing the mainframe to be retired.

{\bf YKK/Message DB} A web development database platform designed for
version reconciliation and replication (in 2005). YKK was the initial
build (in Scheme), Message DB was a rewrite (in Python) which entered
production.

{\bf Coptix Deployment System} A system for automatic deployment of
internal projects, including tools for reconciling SQL schema changes,
software versions, and multiple active deployments. Reproducible
server states allowed some measure of hardware independence prior to
the ubiquity of virtualization.

\end{resume}
\end{document}
